\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-05-25 eg6-letters/NIM/EG6_RTPC_NIM.tex
update figure 12 in the NIM paper
Fix Fig 9

\begin{figure}[tb]
   \centering
   \includegraphics[width=.5\textwidth]{fig/ReadoutScheme.png}
   \caption[]{Schematic representation of the RTPC readout system, showing} 
   \label{fig:ReadoutScheme}
\end{figure}

@@

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.45]{fig_2017/Drift_run_number.pdf}
\caption{$T_{Nbmax/2}$ versus the experimental run numbers (time).  } 
\label{fig:Drift_run_number_1}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.37]{fig/FitResult_p2_10.png}
\caption{$\Delta \phi$ versus T distribution in the second pass for tracks
near 35 mm longitudinal position along the RTPC. The black line represents 
the final drift paths in this slice.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.45]{fig/f_dedx_p_exp_1st.pdf}
   \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
      the RTPC (left) and for the right half (right). Here, 
      $\small{\frac{dE}{dX}}$ is calculated using the gains of the first 
      method.  The lines are theoretical expectations from Bethe-Bloch formula 
   for $^4$He, $^3$He, $^3$H and $^2$H (d).}
\label{fig:dedx_p_exp_1st}
\end{figure}

@@

\begin{figure}[tb]
   \centering
\includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
\caption{Simulated (upper) and experimental (lower) ADC and T distributions 
of a track. The colors indicate the pads, same color in top and bottom indicate 
that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

>>>>

\begin{figure}[tb]
   \centering
   \includegraphics[width=.45\textwidth]{fig/ReadoutScheme.png}
   \caption[]{Schematic representation of the RTPC readout system, showing} 
   \label{fig:ReadoutScheme}
\end{figure}

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=16.5cm]{fig_2017/Drift_run_number.pdf}
\caption{$T_{max/2}$ versus the experimental run numbers.} 
\label{fig:Drift_run_number_1}
\end{figure*}

@@

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.36]{fig/FitResult_p2_10.png}
\caption{$\Delta \phi$ versus T distribution in the second pass for tracks
near 35 mm longitudinal position along the RTPC. The black line represents 
the final drift paths in this slice.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.43]{fig/f_dedx_p_exp_1st.pdf}
   \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
      the RTPC (left) and for the right half (right). Here, 
      $\small{\frac{dE}{dX}}$ is calculated using the gains of the first 
      method.  The lines are theoretical expectations from Bethe-Bloch formula 
   for $^4$He, $^3$He, $^3$H and $^2$H (d).}
\label{fig:dedx_p_exp_1st}
\end{figure}

@@

\begin{figure}[tb]
   \centering
\includegraphics[scale=0.42]{fig_2017/Event_ADC_Graph_8799283.pdf}
\caption{Simulated (upper) and experimental (lower) ADC and T distributions 
of a track. The colors indicate the pads, same color in top and bottom indicate 
that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}
